No need to know: astrophysics-free gravitational-wave cosmology

### 2024-05-15 src/tex/ms.tex
[showyourwork] overleaf sync

This study was carried out using the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork} \citep{Luger2021}, which leverages continuous integration to programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript.
The icons next to each Figure caption are hyperlinks that lead to the code used to make that Figure (github icons), and to the data behind the Figure (cylindrical icons).
Some programatically-generated numbers in the text also have these icons, which function in the same way.
We encourage readers to click these hyperlinks to verify or reproduce the results and methods of this work. The git repository associated to this study is publicly available at \GitHubURL{}, which allows anyone to re-build the entire manuscript.

>>>>

This study was carried out using the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork} \citep{Luger2021}, which leverages continuous integration to programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript.
The icons next to each Figure caption are hyperlinks that lead to the code used to make that Figure (github icons), and to the data behind the Figure (cylindrical icons).
Some programatically-generated numbers in the text also have these icons, which function in the same way.
We encourage readers to click these hyperlinks to verify or reproduce the results and methods of this work. The git repository associated to this study allows anyone to re-build the entire manuscript, and is publicly available at \GitHubURL{} and \url{https://zenodo.org/records/11199928}.
